SciPy 1.0---Fundamental Algorithms for Scientific Computing in Python

### 2019-02-01 scipy-1.0/ckdtree.tex
MAINT: revisions based on PR 91 feeback
* Fix placement of Figure S1 / knn complexity
after rebase / conflict resolution

* revisions to cKDTree knn algorithm paragaph
based on feedback in PR

Specifically, in 2015, we enhanced \texttt{cKDTree.query} by reimplementing in C++,
removing some of the algorithm memory leaks, and allowing 
release of the GIL so that multiple threads may be used\cite{gh-4374}. In 2013,
the time complexity of the k nearest neighbor search from \texttt{cKDTree.query}
was approximately loglinear \cite{knn-jake}, and we've confirmed that this time
complexity has been preserved in SciPy \texttt{1.0.0} (Figure~\ref{fig:knn-complexity}),
but with generally improved efficiency (Figure~\ref{fig:asvbench}). The
discussion in the originally-cited nearest neighbor search
algorithm publication\cite{kdtree-search-algo}, suggests that there are
at least some scenarios where $O(log n)$ search time complexity may
be achieved, but the influence of dimensionality appears to be consistent
with our empirical observations of approximately $0(n log n)$ performance.

>>>>

In 2013, the time complexity of the k nearest neighbor search from
\texttt{cKDTree.query} was approximately loglinear \cite{knn-jake},
consistent with its formal description \cite{kdtree-search-algo}.
Since then, we've enhanced \texttt{cKDTree.query} by reimplementing in
C++, removing memory leaks, and allowing release of the GIL so that
multiple threads may be used\cite{gh-4374}. This generally improved
performance on any given problem (Figure~\ref{fig:asvbench}) while
preserving the asymptotic complexity (Figure~\ref{fig:knn-complexity}).
